---
title: "PowerPoint"
author: "Daniel Xie"
date: "2018/11/22"
output: 
  powerpoint_presentation:
    reference_doc: my-styles.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## multi-column layout
:::::: {.columns}
::: {.column width="50%"}
```{r,echo=TRUE}
head(women)
```
:::
::: {.column width="50%"}
```{r}
plot(women,col="blue",pch = 16,cex = 1.5)
abline(lm(women$weight~women$height),lty=2,lwd=2,col='red')
```
:::
::::::